---
title: "Assessing OBFUSCATED and OBFUSCATED OBFUSCATED in Clinical Trials"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE} 
library(tidyverse)
library(xml2)
library(devtools)
library(RPostgreSQL)
library(ggplot2)
library(ggpubr)
library(scales)
library(data.table)
library(magrittr)
library(rentrez)
```

In order to gauge which OBFUSCATEDs and treatments are potentially most relevant, data from clinicaltrials.gov has been digested and visualized.

## Identifying Relevant Trials

The exact query used to identify relevant trials is:
`AREA[OverallStatus] EXPAND[Term] COVER[FullMatch] "Completed" AND AREA[ResultsFirstSubmitDate] NOT MISSING AND AREA[StudyType] EXPAND[Term] COVER[FullMatch] "Interventional" AND`\n `AREA[ConditionSearch] OBFUSCATED AND AREA[InterventionSearch] OBFUSCATED`

In plain English, this is a search for interventional clinical trials that have completed enrollment, have results, contain the keyword 'OBFUSCATED' and the OBFUSCATED is a OBFUSCATED.

In total, this returned OBFUSCATED studies.

Rather than try to parse the XML into flat files, grab just the NCT IDs 
```{r, results="hide"}
nct_ids = c()
for(i in list.files(path = "OBFUSCATED", full.names = T)){
  f = read_xml(i)
  nct_ids <- c(nct_ids, xml_text(xml_find_all(f, "//nct_id")))
}
write.table(nct_ids, file =  "OBFUSCATED", sep = ",",row.names = F)
```

### The AACT CTTI Database is continuously updated with all clinical trial data from clinicaltrials.gov
```{r}
drv <- dbDriver('PostgreSQL') 
con <- dbConnect(drv, dbname="aact",host="aact-db.ctti-clinicaltrials.org", port=5432, user="scrichman", password="RGHAACT!$")
trial_details <- dbGetQuery(con, paste0("select distinct * from studies where nct_id in ('",paste(nct_ids, sep = "", collapse = "\',\'"),"')"))
intervention_details <- dbGetQuery(con, paste0("select distinct * from interventions where nct_id in ('",paste(nct_ids, sep = "", collapse = "\',\'"),"')"))
reference_details <- dbGetQuery(con, paste0("select distinct * from study_references where nct_id in ('",paste(nct_ids, sep = "", collapse = "\',\'"),"')"))
condition_details <- dbGetQuery(con, paste0("select distinct * from conditions where nct_id in ('",paste(nct_ids, sep = "", collapse = "\',\'"),"')"))
outcome_details <- dbGetQuery(con, paste0("select distinct * from outcomes where nct_id in ('",paste(nct_ids, sep = "", collapse = "\',\'"),"')"))
analysis_details <- dbGetQuery(con, paste0("select distinct * from outcome_analyses where nct_id in ('",paste(nct_ids, sep = "", collapse = "\',\'"),"')"))

dbDisconnect(con)

# Prevent errors such as "OBFUSCATED OBFUSCATED" vs "OBFUSCATED OBFUSCATED"
trial_details %<>% mutate_at(vars(-("nct_id")), tolower)
intervention_details %<>% mutate_at(vars(-("nct_id")), tolower)
condition_details %<>% mutate_at(vars(-("nct_id")), tolower)
reference_details %<>% mutate_at(vars(-("nct_id")), tolower)
condition_details %<>% mutate_at(vars(-("nct_id")), tolower)
outcome_details %<>% mutate_at(vars(-("nct_id")), tolower)
```

## Identifying PubMed entries associated with OBFUSCATED clinical trials using paclitaxel:

First, need to filter for only the relevant NCT IDs
```{r}
cond_filt <- condition_details %>% 
  filter(stringr::str_detect(name, 'OBFUSCATED OBFUSCATED')) 

intv_filt <- intervention_details %>% 
  filter(stringr::str_detect(name, 'paclitaxel'))

in_both <- intersect(cond_filt$nct_id, intv_filt$nct_id)
```

There are OBFUSCATED clinical trials for OBFUSCATED using OBFUSCATED
The references attached to these trials can be retrieved from `reference_details`
```{r}
citations <- reference_details %>% filter((nct_id %in% in_both))
```

There are references that contain PMIDs
```{r}
pmids <- citations %>% filter(!is.na(pmid)) %>% pull(pmid)
```

Unsurprisingly, clinical trial did not publish transcriptomic data or otherwise\n
Results for the clinical trials are available, but clin trial data will be most useful for identifying OBFUSCATED / OBFUSCATED
```{r}
web_history <- entrez_post("pubmed", id=pmids)
summaries <- entrez_summary(db = "pubmed", web_history = web_history)
link <- entrez_link(dbfrom = "pubmed", web_history = web_history, db="sra") # does not link to biosample, bioproject, nucleotide, etc., either
```

OBFUSCATED have been excluded from the below plots because they are OBFUSCATED and highly prevalent in OBFUSCATED
```{r fig.width=8, fig.height=10, echo=FALSE}
trial_details$completion_date <- as.Date(trial_details$completion_date)

filt <- trial_details %>% 
  filter(!is.na(completion_date))

date_hist <- 
  ggplot(filt, aes(x = completion_date)) +
  geom_histogram() +
  theme_pubclean()

date_hist

OBFUSCATED_counts <- intervention_details %>% 
  group_by(name) %>%
  count() %>% 
  arrange(-n) %>%
  filter(stringr::str_detect(name, "OBFUSCATED", negate = T)) %>%
  head(50)

OBFUSCATED_count_plt <- 
  ggplot(OBFUSCATED_counts, aes(x=reorder(name, -n), y=n)) +
  geom_bar(stat="identity") + 
  theme_pubclean() +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "OBFUSCATED",
       y = "Count",
       title = "OBFUSCATED")

OBFUSCATED_count_plt

cond_counts <- condition_details %>% 
  group_by(name) %>%
  count() %>% 
  arrange(-n) %>%
  filter(stringr::str_detect(name, 'OBFUSCATED', negate = T)) %>%
  head(50)

cond_count_plt <- 
  ggplot(cond_counts, aes(x=reorder(name,-n), y=n)) +
  geom_bar(stat="identity") +
  theme_pubclean() +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "Condition",
       y = "Count",
       title = "Number of Clinical Trials by OBFUSCATED")

cond_count_plt

int_by_cond <- merge(intervention_details, condition_details, by = "nct_id")
int_by_cond %<>% rename(OBFUSCATED = name.x, condition = name.y) %>%
  group_by(condition, OBFUSCATED) %>% 
  count() %>%
  arrange(-n) %>%
  filter(stringr::str_detect(condition,  'OBFUSCATED', negate = T)) %>%
  filter(stringr::str_detect(OBFUSCATED, "OBFUSCATED", negate = T)) %>%
  filter(condition %in% c("OBFUSCATED")) %>%
  filter(n > 10) %>%
  ungroup() %>%
  arrange(condition, desc(n)) %>%
  mutate(order = row_number())

int_facet_cond <- 
  ggplot(int_by_cond, aes(x=order, y=n)) +
  geom_bar(stat="identity") +
  theme_pubclean() +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "OBFUSCATED",
       y="Count",
       title = "Distribution of OBFUSCATED by Condition") +
  facet_wrap("condition", scales = "free") + 
  scale_x_continuous(
    breaks = int_by_cond$order,
    labels = int_by_cond$OBFUSCATED,
    expand = c(0,0)
  )
  
int_facet_cond
```

If we're interested in OBFUSCATED, we can filter for common grouping words / symbols.\n
This isn't a perfect method, since some trials use OBFUSCATED.\n
`'with'` and `'and'` are the most likely to return actual OBFUSCATED.
```{r}
OBFUSCATED_ints <- intervention_details %>%
  filter(stringr::str_detect(name, "with|,|and\\b"))

multi_con <- merge(OBFUSCATED_ints, condition_details, by = "nct_id")
multi_con %<>% rename(OBFUSCATED = name.x, condition = name.y)
```

```{r, include=FALSE}
# This uses IDs obtained from the recognized term OBFUSCATED but doesn't seem to be very accurate
nct_ids_md = c()
for(i in list.files(path = "OBFUSCATED",full.names = T)){
  f = read_xml(i)
  nct_ids_md <- c(nct_ids_md, xml_text(xml_find_all(f, "//nct_id")))
}
write.table(nct_ids_md, file =  "OBFUSCATED", sep = ",",row.names = F)

drv <- dbDriver('PostgreSQL') 
con <- dbConnect(drv, dbname="aact",host="aact-db.ctti-clinicaltrials.org", port=5432, user="REDACTED", password="REDACTED")
OBFUSCATED_td <- dbGetQuery(con, paste0("select distinct * from studies where nct_id in ('",paste(nct_ids_md, sep = "", collapse = "\',\'"),"')"))
OBFUSCATED_id <- dbGetQuery(con, paste0("select distinct * from interventions where nct_id in ('",paste(nct_ids_md, sep = "", collapse = "\',\'"),"')"))
OBFUSCATED_rd <- dbGetQuery(con, paste0("select distinct * from study_references where nct_id in ('",paste(nct_ids_md, sep = "", collapse = "\',\'"),"')"))
OBFUSCATED_cd <- dbGetQuery(con, paste0("select distinct * from conditions where nct_id in ('",paste(nct_ids_md, sep = "", collapse = "\',\'"),"')"))
OBFUSCATED_od <- dbGetQuery(con, paste0("select distinct * from outcomes where nct_id in ('",paste(nct_ids_md, sep = "", collapse = "\',\'"),"')"))
OBFUSCATED_ad <- dbGetQuery(con, paste0("select distinct * from outcome_analyses where nct_id in ('",paste(nct_ids_md, sep = "", collapse = "\',\'"),"')"))

dbDisconnect(con)

# Prevent errors such as "OBFUSCATED OBFUSCATED" vs "OBFUSCATED OBFUSCATED"
OBFUSCATED_td %<>% mutate_at(vars(-("nct_id")), tolower)
OBFUSCATED_id %<>% mutate_at(vars(-("nct_id")), tolower)
OBFUSCATED_cd %<>% mutate_at(vars(-("nct_id")), tolower)
OBFUSCATED_rd %<>% mutate_at(vars(-("nct_id")), tolower)
OBFUSCATED_cd %<>% mutate_at(vars(-("nct_id")), tolower)
OBFUSCATED_ad %<>% mutate_at(vars(-("nct_id")), tolower)
```

If we want transcriptomic data, cell lines may be unavoidable.\n
E.g. The OBFUSCATED Lab from OBFUSCATED recently published OBFUSCATED results on OBFUSCATED tested against OBFUSCATED
```{r}
OBF_sum <- entrez_summary(db = "bioproject", id = "OBFUSCATED")
OBF_sum$project_description

```

Find all SRA IDs for the data from the project. \n
These are most easily downloaded with external SRA-tools
```{r}
OBF_sra_link <- entrez_link(dbfrom = "bioproject", id="OBF", db="sra")
sra_ids <- OBF_sra_link$links$bioproject_sra_all
length(sra_ids)
```

## Shared OBFUSCATEDs 
```{r}
OBFUSCATED_OBFUSCATEDs <- c("OBFUSCATED")

OBF_supp_23 <- readxl::read_excel("data/OBF.xlsx", sheet=1, skip=2)
OBF_OBFUSCATEDs_23 <- OBF_supp_23 %>% pull(Name) %>% unique
OBF_supp_95 <- readxl::read_excel("data/OBF.xlsx", sheet=2, skip=2)
OBF_OBFUSCATEDs_95 <- OBF_supp_95 %>% pull(Name) %>% unique

```